Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analyst | AI&nbsp;&&nbsp;DH&nbsp;instructor </font>

### 2023-12-14 index.Rmd
talk

- Talk at the [Cultural Data Analytics Conference 2023](https://cudan.tlu.ee/conference/) 14.12.2023 on using LLMs in a systematic mixed methods framework for large scale humanities & social science research | [slides](https://andreskarjus.github.io/talks/LLMs_humanities_talk_CUDAN2023_AndresKarjus)

>>>>

- Talk at the [Cultural Data Analytics Conference 2023](https://cudan.tlu.ee/conference/) 14.12.2023 on using LLMs in a systematic mixed methods framework for large scale humanities & social science research | [slides](https://andreskarjus.github.io/talks/LLMs_humanities_talk_CUDAN2023_AndresKarjus.pdf)
